Reconstructing Propositional Proofs in Type Theory

### 2017-12-17 paper/sections/type-theory.tex
fixed some spacing issues.

\begin{notation}
  We use \Prop for the type of propositions.
  A proposition is an expression of indivisible propositional variables (\eg, symbols $φ₀, φ₁, \cdots$), the logic constants:
  $⊥$, $⊤$, the binary connectives ($∧, ∨, ⇒)$, and the negation
  $(\neg)$. We use the inductive definition for propositions presented in~\cite{VanDalen1994}.

  We write the syntactical equality using the symbol (≡) as $φ ≡ ψ$, for $φ,~ψ :
  \Prop$. For this equality, we assume the reflexivity, symmetry and
  transitivity properties.
  % We say $φ$ and $ψ$ are syntactically equivalent if there is a derivation from $φ$ to $ψ$ and
  % a derivation from $ψ$ to $φ$.
  The type of natural numbers is called \Nat,
  and it is defined as usual, where $\zero$ and $\suc$ are its data
  constructors. We use names and symbols for the arithmetic operations
  as usual (\eg, $+$, $-$, $*$).  We use syntax sugar for $\zero$, $\suc$,
  $\suc~\zero$, $\dots$, with the decimal representation~$0$, $1$,
  $2$, $\dots$ as well.
\end{notation}

Hence, one approach to define a structural recursive function based
on a general
recursive function $\rm{f}:\,\type{A}~\to~\type{B}$ is to
formulate a new
function $\rm{f}^{*}:\,\type{A}~\to~\Nat~\to~\type{B}$ where all
of its recursive calls are done on smaller arguments.

>>>>

\begin{notation}
  We use \Prop for the type of propositions.
  A proposition is an expression of indivisible propositional variables (\eg, symbols $φ₀, φ₁, \cdots$), and the logic constants:
  $⊥$, $⊤$, the binary connectives ($∧, ∨, ⇒)$, and the negation
  $(\neg)$. We use the inductive definition for propositions presented in~\cite{VanDalen1994}.

  We write the syntactical equality between two propositions φ and ψ using the symbol (≡) as $φ ≡ ψ$. For this equality, we assume the reflexivity, symmetry and
  transitivity properties.

  The type of natural numbers is called \Nat,
  and it is defined as usual, \ie, $\zero$ and $\suc$ are its data
  constructors. We use names and symbols for the arithmetic
  operations as usual (\eg, $+$, $-$, $*$).
  We use syntax sugar for $\zero$, $\suc$,
  $\suc~\zero$, $\dots$, with the decimal representation~$0$, $1$,
  $2$, $\dots$ as well.
\end{notation}

Hence, one approach to define a structural recursive function based
on a general
recursive function $f₀ : \type{A} \to \type{B}$ is to
formulate a new
function $f₁ : \type{A} \to \Nat \to \type{B}$ where all
of its recursive calls are done on smaller arguments.
